\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-12-03 Final Paper/PaperJLin.tex
Added Electoral Formula NEW interpretation

From the results that reflects general trends in the world based on the new liberalism variable, we see that there are some differences between place of residence and issue stances. Looking at Table \ref{table14} alongside the earlier Table \ref{table3}, we see that there urban-rural divide is more pronounced than it was before. (Both Tables are reproduced in Appendix \ref{AppendixD} for simplicity in comparison)

However, the results here provide an interesting deviation from the patterns that are observed using self-placement on the ideology spectrum as a dependent variable. Here, a higher score indicates that individuals will be \e{more} liberal when it comes to government spending on social policy. As noted earlier, residents of urban centers tend to see themselves as more left-leaning, but they are relatively less interested in seeing government spend more money on health care, defense, and other social welfare measures that would ensure equity among the people in the country.

@@

The data in Table \ref{table15} suggests that there is a difference between urban and rural residents when it comes to spending, but this pattern is not as emphasized in self-placement ideology. The results of this model confirms the work from previous literature to show that urban residents are more open to government spending to help a neighbor than residents in a rural area of a country. Yet, the interesting difference lies in the breakdown of self-placement on the ideology spectrum. While there is not as much significance between urban and rural residents, there are differences with each of the residence types that can be analyzed further.

@@

Majoritarian elections are defined by first-past-the-post result tabulations where the candidate with the most votes is tapped as the winner of the race. With this campaign method, there is space of candidates to appeal to certain constituencies strategically to gain the most votes for themselves. In theory, a large representative body should serve different interests, but reality is hard to match expectations. Therefore, candidates and voters alike must push for their own interests to dominate, making a polarized electorate more likely on the lines of differing interest \cite{abramowitz-2010}. The results confirms this expectation. Individuals living in small towns, suburban and urban areas are significantly mor likely to lean left than their rural counterparts. While the differences among each other is not as big of a difference, it is significantly different from a rural place of residence.

Proportional representation occurs when parties are able to allocate votes in ratio to the number of votes that they receive. Therefore, it becomes more likely that different interests are represented in practice and that minority parties will have a chance in policymaking. This may help explain the insignificant results for the differences in places of residence on political attitudes when the countries are aggregated. However, in our previous discussions, proportional countries also see significant differences between places of residence, with Israel and Greece in 2012. However, this aggregate pattern carries for most of the other proportional representation states in this study.

Finally, a mixed representation system has combinations of the aforementioned systems. When aggregated, there are differences between place of residence and political attitudes. Depending on the specifications of the government design in each country, there can be great variations between countries and levels of significance. While the urban-rural divide is significant in Germany, it is not so in Japan.

To conclude, we see that the electoral formula matters in shaping political competition and electoral appeals from the perspective of the party. However, there are not clear distinctions for formulas such that it is a tell-all third factor in explaining the relationship between place and political attitudes.

>>>>

From the results that reflects general trends in the world based on the new liberalism variable, we see that there are some differences between place of residence and issue stances. Looking at Table \ref{table14} alongside the earlier Table \ref{table3}, we see that there urban-rural divide is less pronounced than it was before. (Both Tables are reproduced in Appendix \ref{AppendixD} for simplicity in comparison). The results here parallel the findings in the self-placement ideology analyses. Here, on a worldwide scale, respondents who live in an urban area are more likely to lean conservative but the tilt towards conservatism is not as great of a point jump compared to the self-placement ideology as a dependent variable. This suggests that people may, on average, place themselves farther to the right or left, but this feeling of placement on the spectrum is not entirely reflected in the way they truly view the issues.

@@

The data in Table \ref{table15} suggests that there is a difference between urban and rural residents when it comes to self-placement ideology, but this effect is not highlighted as well when it comes to views on government spending. The results of this model confirms the work from previous literature to show that urban residents are less open to government spending to help a neighbor than residents in a rural area of a country. We do not see the same level of significance for conservative or liberal issue stances as we do in self-placement on the ideological spectrum. Therefore, when we consider the macro variables, urban residents will, in general, place themselves more to the right than what is reflected by their issue stances, and this observation is not seen from chance alone.

@@

Majoritarian elections are defined by first-past-the-post result tabulations where the candidate with the most votes is tapped as the winner of the race. With this campaign method, there is space of candidates to appeal to certain constituencies strategically to gain the most votes for themselves. In theory, a large representative body should serve different interests, but reality is hard to match expectations. Therefore, candidates and voters alike must push for their own interests to dominate, making a polarized electorate more likely on the lines of differing interest \cite{abramowitz-2010}. The results confirms this expectation. Individuals living in small towns, suburban and urban areas are more likely to lean left than their rural counterparts. However, from the results shows in Table \ref{table15}, only urban residents have statistical significance compared to their rural counterparts, but it is over a third of a point to the left, making that a moderate influence. Despite the aggregated statistical significance, it is also important to note that this pattern is not present for all majoritarian systems when broken down. The only country where this same pattern is seen is in France. Other majoritarian countries may see a move in this general direction, but not to the extent of statistical significance.

Proportional representation occurs when parties are able to allocate votes in ratio to the number of votes that they receive. Therefore, it becomes more likely that different interests are represented in practice and that minority parties will have a chance in policy-making. Yet the results suggest that there is a rural-urban divide among the respondents, and this effect is present in all areas of residence studied in this analysis. From the results, we see that there is a trend towards conservatism, even if it is more pronounced in small towns compared to rural areas than in urban centers compared to rural areas. Yet, while the aggregate tells this picture, there are also proportional systems that confirm the |e{Self-Identified Ideology} hypothesis, namely Greece in 2012 and South Africa. There are proportional systems that may move in the direction of the aggregate but the observations may occur due to chance.

Finally, a mixed representation system has combinations of the aforementioned systems. When aggregated, there are differences between place of residence and political attitudes. Much like the results in a proportional system, the responses for urban residents are over a half a point to the right, which is a relatively significant amount for countries in this system. This trend goes against the observations of Mexico in their 2015 electon, even if it confirms the patterns of Romania in 2012.

To conclude, we see that the electoral formula matters in shaping political competition and electoral appeals from the perspective of the party. However, there are not clear distinctions for formulas such that it is a tell-all third factor in explaining the relationship between place and political attitudes. When aggregated, we find differing results than when the countries are broken down, showing that an aggregration of an effect does not indicate how the specifications of polity uniqueness may play out.
